---
title: "Session 1 - Homework"
#output: html_notebook
---

  
Set working directory:
```{r}
setwd("/Users/demian/Desktop/data_science")
getwd()
```

Load required packages:
```{r}
library(tidyverse)
library(readr)
```

Import datasets:
```{r}
books <- read_delim("BX-Books.csv", 
    ";", escape_backslash = TRUE, escape_double = FALSE, 
    trim_ws = TRUE)
View(books)

# users <- read_delim("BX-Users.csv", 
#     ";", escape_backslash = TRUE, escape_double = FALSE, 
#     trim_ws = TRUE)
# View(users)

ratings <- read_delim("BX-Book-Ratings.csv", 
    ";", escape_backslash = TRUE, escape_double = FALSE, 
    trim_ws = TRUE)
View(ratings)
```

Clean data: use valid ISBNs only

a) ratings: delete non-numeric characters from string and strings with length < 10
```{r}
ratings$ISBN <- gsub("[^0-9]", "", ratings$ISBN) 

sum(str_length(ratings$ISBN) == 10)
ratings %>%
  count(str_length(ISBN)==10) 

# numbers_only <- function(x) !grepl("\\D", x)
# sum(numbers_only(ratings$ISBN)==TRUE)
# ratings %>%
#   count(numbers_only(ISBN)==TRUE) 

ratings <- ratings %>%
  filter(str_length(ISBN) == 10)
#View(ratings)

```

b) books: delete non-numeric characters from string and strings with length < 10
```{r}
books$ISBN <- gsub("[^0-9]", "", books$ISBN) 

books <- books %>%
  filter(str_length(ISBN) == 10)
#View(books)
```

Match datasets books and ratings:
```{r}
books_w_ratings <- books %>%
  left_join(ratings)
```

#Question 1: Welche Bücher sind am besten bewertet?
```{r}
hist(books_w_ratings$`Book-Rating`)
hist(books_w_ratings$`Book-Rating`[books_w_ratings$`Book-Rating`!=0])
summary(books_w_ratings$`Book-Rating`)
sum(books_w_ratings$`Book-Rating` == 0, na.rm = TRUE)
sum(books_w_ratings$`Book-Rating` != 0, na.rm = TRUE)
sum(is.na(books_w_ratings$`Book-Rating`))
length(unique(books_w_ratings$ISBN))

books_w_ratings %>%
  group_by(ISBN) %>%
  summarise(gesamtbewertung = mean(`Book-Rating`)) %>% 
  arrange(desc(gesamtbewertung))
```


#Question 2: Sollte die Anzahl der Bewertungen auch mit reinspielen?
```{r}
books_w_ratings %>%
  group_by(ISBN) %>%
  summarise(gesamtbewertung = mean(`Book-Rating`), anzahl_bewertungen = n()) %>% 
  arrange(desc(gesamtbewertung), desc(anzahl_bewertungen))
```

# Question 3: Welche Autoren sind am besten bewertet?
```{r}
books_w_ratings %>%
  group_by(`Book-Author`) %>%
  summarise(gesamtbewertung = mean(`Book-Rating`)) %>% 
  arrange(desc(gesamtbewertung))
```


# Question 4: Welcher Verlag hat die besten Bücher?
```{r}
books_w_ratings %>%
  group_by(`Publisher`) %>%
  summarise(gesamtbewertung = mean(`Book-Rating`)) %>% 
  arrange(desc(gesamtbewertung))
```


